\begin{itemize}
    \item Develop a PCB for the electronics to mitigate potential issues and eliminate current problems. Currently, connecting IDC 2 with the power off results in the motor drivers drawing power from the Arduino, which poses a risk of damage to the MCU and the computer. The underlying cause of this issue remains elusive.
    
    \item When establishing serial communication with the Arduino, the LED linked to pin \texttt{D13} blinks twice. This indicates that the power to the motors must be off or that another PWM pin must be utilized when connecting the module.
    
    \item It is recommended that the joystick functionality be implemented for direct control. The objective of this feature was to facilitate the simultaneous adjustment of all actuators, which would in turn assist with the insertion and removal of rods.
    
    \item Complete the implementation of missing command functionalities in the control language.
    
    \item Enhance the design of actuators to streamline assembly. The current placement of screws securing actuators to the base is inaccessible and cumbersome.
    
    \item Address challenges with spring installation and adjustability. Utilize mathematical models or adopt extruder-like systems to regulate spring tension effectively.
    
    \item Refine model tolerances to improve alignment of the rod with bearings and drive pulleys. Explore alternative materials or manufacturing methods to rectify identified defects in the actuator design for 3D printing.
    
    \item Enhance portability by transitioning the system from mains power to battery operation.
    
    \item Develop a static or kinetic model of the robot using analytical methods or machine learning algorithms, leveraging the platform and robot for practical applications.
\end{itemize}